\documentclass{article}
\usepackage[letterpaper,margin=1.0in]{geometry}
\usepackage{setspace}
\usepackage[pdftex]{graphicx}
\begin{document}
\title{Knowledge Advantage Desktop: Interface, Infrastructure, and Markup}
\author{Larry Reaves}
\maketitle
\pagebreak
\begin{doublespace}
\section{Introduction}
In modern times, we are inundated with a huge amount of information for a wide range of sources.
While making sense of this firehose of knowledge can be quite a challenge, it is essential to be able
to function in many of today's work environments.
Knowledge Advantage Desktop (KAD) is a tool for discovering information, extracting meaning,
finding connections between different pieces of information,
and visualizing the knowledge that has been processed.
\par
By leveraging KAD, a knowledge worker is able to more quickly find information that is relavant to their
work by inputing search parameters.
After the software finds a piece of information matching the search parameters,
it will extract important words from the text as well as other information such as the author or date of publication.
Combined, the document and these annotations make up what we call a JAN.
These JANs are then networked by finding common metadata such as keywords or authors.
This network is visualized so that the user can easily move from one document to related documents.
The network can also be searched to find a particular keyword or author.
\par
A group of networked JANs is called a JANBase.
KAD supports the ability to switch between JANBases so that you can have separate networks for different topics.
This makes it easier to find information relavent to your current work objective.
\section{Interface}
The KAD interface has three main sections.
$<$insert screen capture$>$
On the left is the Editor Pane (EP).
The EP is intended for content production.
It allows you to edit any text file, from programming source code to TeX markup.
In the case of TeX markup, there is a {\it "Render"} button that will generate a PDF document.
This PDF will be shown in the lower left pane, which we call the Knowledge Pane (KP).
The KP will show both web sites as well as PDF documents.
At the top of the KP is the location bar, which allows you to directly navigate to any url or PDF file.
When browsing web sites, if a PDF link is selected, the PDF is automatically downloaded and displayed
in the KP.
If the current document being shown in the KP does not have an existing JAN, there will be a
{\it "Make JAN"} button displayed.
This button allows the user to create a JAN from the window's current contents,
facilitating manual discovery in addtion to the automated discovery provided by the web crawler.
Above the KP is the Visualization Pane (VP).
The VP allows the user to visualize and search their current JANBase.
In addition to the three main sections, there is also a bottom bar consisting of a status area,
a JANBase selection dropdown, and a {\it "Settings"} button.
\par
In the settings, there are two areas: {\it "JANBase"} and {\lt "Discovery Settings"}.
In the "JANBase" section, the user is able to Add, Load, Merge, and Delete JANBases.
In the "Discovery Settings" the user can set up the search parameters for automatic discovery of PDF documents.
\par
There are several keyboard shortcuts available to simplify certain actions within KAD.
\fbox{Control} - \fbox{O} will allow you to select a file to open in the Editor Pane.
\fbox{Control} - \fbox{S} will save the current file in the EP.
\fbox{Control} - \fbox{L} will focus the lation bar within the Knowledge Pane.
\fbox{Control} - \fbox{R} can be used to reload KAD.
This is useful if you have edited the KAD source code and want to restart the application.
\fbox{Control} - \fbox{Q} will shutdown KAD.
\section{Infrastructure}
In order to tie the various parts of the application together,
quite a few automated processes happen behind the scenes.
Depending on which JANBase is selected, there is a folder that contains the raw JANs for newly discovered documents.
There is a watcher thread that checks this folder for new JANs every few seconds.
When a new JAN is found, the document is passed to the markup process.
This process, discribed in the {\it Markup} section below, extends the new JANs with additional metadata gleaned
from interpreting the contents.
The marked up JAN is then placed into another folder.
This folder is watched for changes by the network processing thread.
This thread will connect the marked up JAN to the network for the JANBase.
Additionally, there is another directory watcher thread that will create a new JAN any new PDFs that appear in
the pdf folder for the current JANBase.
Each JANBase is a separate folder, and loading a different JANBase will change the directories that are watched
to the subdirectories within the top level directory for that JANBase. 
\section{Markup}
In KAD, Markup is the process of extracting metadata from discovered documents.
The markup engine supports python files, urls, PDFs, and emails (mbox format).
For all documents, a plain text version is extracted.
This text is then processed to extract key words.
\subsection{Keyword Extraction}

\end{doublespace}
\end{document}
